IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
more outdated terminology.

    \item In the case of mini-ML, type safety proceeds by a preservation theorem
        that refers to well-typed stores.  In our setting, there are now multiple
        stores, and expressions may move from being interpreted with one store
        to another (e.g. when an address is sent from one thread to
        another); a clear violation of type safety.  In this case, operations
        such as \textbf{send} have their typing rules require
        the expressions being sent be typeable in an arbitrary well-typed store,
        statically disallowing the sending of addresses, or any types which
        may contain addresses.  In practice, this may be further restricted to
        types which can be easily marshalled, e.g. strings.

    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
        influences the difficulty of the type-safety proof for
        \textbf{fork} when the target language has a store.  When
        $\kappa$ is identity, most expressions can be allowed, since the store
        remains the same; if $\kappa$ drops the store, however, only closed expressions
        can be forked.
\end{itemize}

>>>>

    \item In the case of mini-ML, type safety proceeds by a preservation theorem
        that refers to well-typed stores.  In our setting, there are now multiple
        stores, and expressions may move from being interpreted with one store
        to another (e.g. when an address is sent from one thread to
        another); a clear violation of type safety.  In this case, operations
        such as |send| have their typing rules require
        the expressions being sent be typeable in an arbitrary well-typed store,
        statically disallowing the sending of addresses, or any types which
        may contain addresses.  In practice, this may be further restricted to
        types which can be easily marshalled, e.g. strings.

    \item Similarly, the choice of $\kappa$ (from Section~\ref{sec:retrofit}) directly
        influences the difficulty of the type-safety proof for
        |sandbox| when the target language has a store.  When
        $\kappa$ is identity, most expressions can be allowed, since the store
        remains the same; if $\kappa$ drops the store, however, only closed expressions
        can be sandboxed.
\end{itemize}
